### 2019-10-11 2019 Journal/introduction.tex
Barely started with an edit and a few comments in the introduction.

Mixed-integer linear programming (MILP), the optimization of a linear objective function subject to linear and integrality constraints, models many practical optimization problems including scheduling, logistics and resource allocation.  The set of feasible points for a MILP is the set
\begin{equation}
S(A,G,b)= \{(x,y)\in \mathbb{Z}^{n}\times \mathbb{R}^p\;:\; Ax+Gy\geq b\}  \label{S}.
\end{equation}
If we drop the integrality constraints, we have the linear relaxation of set $S(A,G,b)$,
\begin{equation}
P(A,G,b) = \{(x,y)\in \mathbb{R}^{n+ p}\;:\; Ax+Gy\geq b\}. \label{P}
\end{equation}

Let $I=(A,G,b)$ be the feasible set of a specific instance. Then $S(I)$ and $P(I)$ denote $S(A,G,b)$ and $P(A,G,b)$, respectively. Given a linear objective function $c$, a Mixed-Integer-Linear Program (MILP) is $\min \;\{cx:\; (x,y) \in S(I)\}$. It is  NP-hard even to determine if an MILP instance has a feasible solution~\cite{GJ79}. However, intelligent branch-and-bound strategies allow commercial and open-source MILP solvers to give exact solutions (or near-optimal with provable bound) to many specific instances of NP-hard combinatorial optimization problems.

Relaxing the integrality constraints gives the polynomial-time-solvable linear-programming relaxation: $\min \;\{cx:\;(x,y)\in P(I) \}$.  The optimal value of this linear program (LP), denoted $z_{LP}(I,c)$, is a lower bound on the optimal value for the MILP, denoted $z_{IP}(I,c)$. The solution can also provide some useful global structure, even though the fractional values are not directly meaningful. {\em LP-based approximation algorithms} for combinatorial problems involve modeling the problem as a MILP, solving the LP relaxation, finding a (problem-specific) integer-feasible solution from the LP solution, and proving an approximation bound by comparing the solution value to the LP lower bound.

>>>>

Mixed-integer linear programming (MILP), the optimization of a linear objective function subject to linear and integrality constraints, models many practical optimization problems including scheduling, logistics and resource allocation.  The set of feasible points for a MILP with $n$ integer variables and $p$ continuous variables is the set
\begin{equation}
S(A,G,b)= \{(x,y)\in \mathbb{Z}^{n}\times \mathbb{R}^p\;:\; Ax+Gy\geq b\}  \label{S}.
\end{equation}
If we drop the integrality constraints, we have the linear relaxation of set $S(A,G,b)$,
\begin{equation}
P(A,G,b) = \{(x,y)\in \mathbb{R}^{n+ p}\;:\; Ax+Gy\geq b\}. \label{P}
\end{equation}

Let $I=(A,G,b)$ be the feasible set \cindy{Should this be ``input?'' The feasible set is a set of ordered pairs $(x,y)$.} of a specific instance. Then $S(I)$ and $P(I)$ denote $S(A,G,b)$ and $P(A,G,b)$, respectively. Given a linear objective function $c$, a Mixed-Integer-Linear Program (MILP) is $\min \;\{cx:\; (x,y) \in S(I)\}$. \cindy{Can't the objective function depend on the continuous variables too?  Sometimes the continuous variables are helper variables for computing the objective. If you are only considering a restricted set of MIPs, then that has to be stated explicitly.  This reads as though this is the general definition.} It is  NP-hard even to determine if an MILP instance has a feasible solution~\cite{GJ79}. However, intelligent branch-and-bound strategies allow commercial and open-source MILP solvers to give exact solutions (or near-optimal with provable bound) to many specific instances of NP-hard combinatorial optimization problems.

Relaxing the integrality constraints gives the polynomial-time-solvable linear-programming relaxation: $\min \;\{cx:\;(x,y)\in P(I) \}$. \cindy{If we allow the orginal continuous variables to contribute to the objective function, this has to change too.} The optimal value of this linear program (LP), denoted $z_{LP}(I,c)$, is a lower bound on the optimal value for the MILP, denoted $z_{IP}(I,c)$. The solution can also provide some useful global structure, even though the fractional values are not directly meaningful. {\em LP-based approximation algorithms} for combinatorial problems involve modeling the problem as a MILP, solving the LP relaxation, finding a (problem-specific) integer-feasible solution from the LP solution, and proving an approximation bound by comparing the solution value to the LP lower bound.
